Supplementary Material

### 2022-11-10 paper/paper/SPIE/article.tex
[WIP]

Summarizing this amount of data requires some caution. Measures of location or
scale, even when robust, are, for the most part, misleading and uninformative
when distributions are skewed. In most cases we find skewed mAUROC
distributions, and so have chosen primarily to present our findings visually.

In addition, each analytic factor could produce an interaction. For example, it
could be that trimming impacts the overall mAUROC distribution only at a
certain preprocessing level and for certain feature slicing. However, there are
too many potential interactions to present, so we limit our presentation
to the most significant ones.

As there are a large number of figures, we summarize patterns of results across
two abstract levels of feature groupings—"coarse", and "fine"—shown in
Table \ref{tab:features}.

@@

@@

\subsection{Effect of Preprocessing}
At a coarse level

  if a certain feature is simply not useful, or if a certain comparison
task is not solvable with some or even all classifiers

@@

\subsection{Classifier}
When the data is predictable, timeseries features almost all have the mode / max <= 0.5 for all
classifiers and subgroups, whereas eigenfeatures (RMT, eigenvalue only, eigenvalue + RMT) more often
than not have mode greater than 0.5, and bulk of the distribution > 0.5.

KNN3 consistently has least favourable AUROC distributions across subgroups and features

\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

\begin{table}[ht]
\caption{Fonts sizes and styles.}
\label{tab:fonts}
\begin{center}
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{mcr3b.eps}
\end{tabular}
\end{center}
\caption
{ \label{fig:example}
Example of a figure caption. }
\end{figure}

Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images
\\
(a) \hspace{5.1cm} (b)
\end{tabular}
\end{center}
\caption
{ \label{fig:example2}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.}
\end{figure}

>>>>

Summarizing this quantity of data requires some caution. Measures of location or
scale, even when robust, are, for the most part, misleading and uninformative
when distributions are skewed. In most cases we find skewed mAUROC
distributions, and so have chosen primarily to present our findings visually,
with kernel density estimates.

In addition, each analytic factor could produce an interaction. For example, it
could be that trimming impacts the overall mAUROC distribution only at a
certain preprocessing level and for certain feature slicing. However, there are
too many potential interactions to present, so we limit our presentation to the
most significant ones.  As there are a large number of features, we also
summarize patterns of results across two abstract levels of feature
groupings—"coarse", and "fine"—shown in Table \ref{tab:features}.

@@

Eigenfeatures most strongly and consistently demonstrated predictive utility
in the \textit{Aging} dataset \code{older v younger} classification task, the
\textit{Osteo} dataset \code{nopain v duloxetine} task, and in the \textit{Attention}
\code{vigilant v nonvigilant} comparison.

@@

\subsection{Largest mAUROCs}
Considering the various analytic choices as tunable parameters, it makes sense
to examine the \textit{largest} portion of mAUROCs as an indication of the
maximum predictive potential of the eigenfeatures. In this case, it is clear
that eigenfeatures using RMT features almost always had the highest potential
predictive utility (Figure \ref{fig:largest}). Figure S\ref{S-fig:fine-largest}
shows that this was primarily due to either the "rmt only" or "rmt + eigs"
features (see Table \ref{tab:features}). However, these features were also most
likely to cause poor performance and overfitting (indicated by an mAUROC \(<\)
0.5; Figure S\ref{S-fig:fine-smallest}).

Examining these RMT features more closely (Figure S\ref{S-fig:fig:fine-degree}),
it is clear these features are more predictive mostly due to the unfolding
procedure: the mAUROC distributions with largest medians and modes are due to
features that include the unfolded eigenvalues. Combined features that use
the unfolded eigenvalues plus some other RMT eigenfeature have identical
mAUROC distributions to those using the unfolded eigenvalues alone.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6.5in]{coarse_feature_largest_by_subgroup.png}
\end{tabular}
\end{center}
\caption
{ \label{fig:largest} Distributions of largest 500 mAUROCs by coarse feature grouping.}
\end{figure}

\subsection{Effect of Preprocessing}
At a coarse level, slice time correction followed by motion correction tended
to slightly increase the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}) relative to brain extraction only. Subsequent registration
following these steps did not generally impact mAUROC distributions further,
except in the \code{task\_attend v task\_nonattend} comparison, where
registration reduced the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}, second-last column). When examining features more finely, it
is clear that preprocessing most impacts the mAUROC distribution of the largest
and central eigenvalues ("eigs middle" and "eigs max" in Figure
S\ref{S-fig:fine-preproc})

\subsection{Effect of Classifier}
mAUROC distributions were generally similar across coarse or fine feature
groupings (Figure S\ref{S-fig:coarse-classifier}, S\ref{S-fig:fine-classifier}).
In the \textit{Attention} \code{task\_attend v task\_nonattend} condition, eigenfeatures were modally predictive only with
the random forest classifier, whereas in the \textit{Aging} data, a SVC was least
likely to have mAUROC \(<\) 0.5. Overall, however, differences in the mAUROC distributions
were small.

\subsection{Effect of Trimming}
Trimming based on numerical precision (see Section \ref{sec:rmt-features} and
Appendix \ref{sec:trimming}), did not result in meaningfully different mAUROC
distributions in any case (Figure S\ref{S-fig:fine-trim}).   While there was no
clearly observable differences between the mAUROC distributions depending on
whether

\subsection{Effect of Unfolding Degree}
The choice of polynomial unfolding degree significantly impacted the mAUROC
distributions for most classification tasks and most RMT features, and most
significantly for the level variance features (Figure
S\ref{S-fig:fine-degree}). Overall, Figure S\ref{S-fig:fine-degree} weakly
suggests that either smaller (degree = 3) or larger (degree = 9) unfolding
degrees tend to yield the most predictively useful RMT features. However, when
restricting to the most predictive RMT features (those including the unfolded
eigenvalues), it seems clear from Figure S\ref{S-fig:fine-degree} the the
largest unfolding degree of 9 produces the most favourable mAUROC
distributions.

@@

% \subsection{Page Setup and Fonts}

% All text and figures, including footnotes, must fit inside a text area 6.5 in.\
% wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US
% letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1
% in.\ on the bottom, and 1 in.\ on the left and right.

% The Times New Roman font is used throughout the manuscript, in the sizes and
% styles shown in Table~\ref{tab:fonts}. If this font is not available, use a
% similar serif font. The manuscript should not contain headers or footers. Pages
% should be numbered.

% \begin{table}[ht]
% \caption{Fonts sizes and styles.}
% \label{tab:fonts}
% \begin{center}
% \begin{tabular}{|l|l|} %% this creates two columns
% %% |l|l| to left justify each column entry
% %% |c|c| to center each column entry
% %% use of \rule[]{}{} below opens up each row
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
% \hline\hline
% \rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
% \hline
% \rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
% \hline
% \end{tabular}
% \end{center}
% \end{table}

@@

% \begin{figure}
% \begin{center}
% \begin{tabular}{c}
% \includegraphics[height=5.5cm]{mcr3b.eps}
% \end{tabular}
% \end{center}
% \caption
% { \label{fig:example}
% Example of a figure caption. }
% \end{figure}

% Authors may wish to create figures consisting of two or more images, in which
% case, they should be neatly arranged in a rectangular array.  In no case,
% should the article's text be wrapped around a figure. Figure~\ref{fig:example2}
% shows two side-by-side images. When a figure contains more than one image, the
% author must submit them as a single image file. Further details about figure
% formatting can be found in the author guidelines for each specific SPIE
% journal: \\

% \linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.

% \begin{figure}
% \begin{center}
% \begin{tabular}{c}
% \includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images
% \\
% (a) \hspace{5.1cm} (b)
% \end{tabular}
% \end{center}
% \caption
% { \label{fig:example2} Example of a figure containing multiple images: (a) sun
% and (b) blob. Figures containing multiple images must be submitted to SPIE as a
% single image file.}
% \end{figure}

### 2022-11-10 paper/paper/SPIE/supplementary.tex
[WIP]

% \documentclass[12pt]{supplementary}  % 12pt font required by SPIE;
\documentclass{article}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{authblk}
\usepackage{times}
\usepackage{float}
\usepackage{ifthen}
\usepackage{setspace}
\usepackage[super]{cite}[2003/11/04] % need vers. > 4.01
\usepackage{color}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{pdflscape}
\usepackage{geometry}
\geometry{
  textwidth=11in,
  textheight=8.5in,
  headheight=0in,
  headsep=0in,
  marginparwidth=0in,
  papersize={11in,8.5in},
  left=0in,
  lmargin=0in,
  inner=0in,
  right=0in,
  rmargin=0in,
  outer=0in,
  top=0in,
  tmarg=0in,
  bottom=0in,
  bmargin=0in,
}

@@

>>>>

\documentclass{article}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{authblk}
\usepackage{times}
\usepackage{float}
\usepackage{ifthen}
\usepackage{setspace}
\usepackage[super]{cite}[2003/11/04] % need vers. > 4.01
\usepackage{color}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{doi}
\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage{pdflscape}
\usepackage{geometry}
\geometry{
  textwidth=11in,
  textheight=8.5in,
  headheight=0in,
  headsep=0in,
  marginparwidth=0in,
  papersize={11in,8.5in},
  left=0in,
  lmargin=0in,
  inner=0in,
  right=0in,
  rmargin=0in,
  outer=0in,
  top=0in,
  tmarg=0in,
  bottom=0in,
  bmargin=0in,
}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{coarse_feature_group_by_predictive_subgroup_classifier.png}
\end{center}
\caption
{ \label{fig:coarse-classifier}
AUROC distributions across coarse feature groupings and predictable comparison tasks, by classifier.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{fine_feature_group_by_predictive_subgroup_classifier.png}
\end{center}
\caption
{ \label{fig:fine-classifier}
AUROC distributions across coarse feature groupings and predictable comparison tasks, by classifier.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{fine_feature_largest_by_subgroup.png}
\end{center}
\caption
{ \label{fig:fine-largest}
Distributions of largest 500 mAUROCs across fine feature grouping, by comparison task.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{fine_feature_smallest_by_subgroup.png}
\end{center}
\caption
{ \label{fig:fine-smallest}
Distributions of smallest 500 mAUROCs across fine feature groupings, by comparison task.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{rmt_feature_auroc_by_trim.png}
\end{center}
\caption
{ \label{fig:fine-trim}
Distributions of mAUROCs for unfolding-dependent RMT features, by degree.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{rmt_feature_auroc_by_degree.png}
\end{center}
\caption
{ \label{fig:fine-degree}
Distributions of mAUROCs for unfolding-dependent RMT features, by degree.}
\end{figure}
